Matching Bullets

### 2015-12-09 imaging-paper.Rnw
another picture: mismatch with CMS 15

>>>>

\begin{figure}
<<strange-res, echo=FALSE, fig.width=7, fig.height=4, out.width='\\linewidth'>>=
load("data-35-25/unkn82.RData")
res <- reslist[[97]]

print(ggplot() +
  theme_bw() + 
  geom_rect(aes(xmin=xmin, xmax=xmax, fill=factor(type)), ymin=-6, ymax=5, data=res$lines, alpha=0.2, show.legend=FALSE) +
  geom_line(aes(x = y, y = l30, linetype = bullet),  data = res$bullets) +
#  geom_hline(yintercept = res$threshold) +
#  geom_hline(yintercept = - res$threshold) +
#  scale_colour_brewer("",palette="Set1") +
  scale_linetype_discrete("") +
  scale_fill_brewer("", palette="Set2", na.value=alpha("grey50", alpha=0.5)) +
  theme(legend.position = c(1,1), legend.justification=c(1,1)) + 
  ylim(c(-6,6)) +
  geom_text(aes(x = meany), y= -5.5, label= "x", data = subset(res$lines, !match)) +
  geom_text(aes(x = meany), y= -5.5, label= "o", data = subset(res$lines, match)))
@
\caption{\label{fig:mismatch}Known mismatch with a surprisingly large number of maximal consecutive matching striae (fifteen) and a small distance between the crosscuts. }
\end{figure}
